---
output:
  pdf_document: default
  html_document: default
---
```{r}
property = read.csv("R Programming/DOF__Condominium.csv")
property
```
**Multivariate**
**Estimated Gross Income,Full Market Value & Estimated Expense **
**Estimated Gross Income= 0.59203 * Full Market Value  + 0.41266 Estimated Expense - 0.5288**
**It means Estimated Gross Income increases 0.59 times of Full Market Value and 0.41 times of Estimated Expense. This multivariate is showing positive relation with 99% Multiple R Sqaured**

```{r}
mymodel = lm(Estimated.Gross.Income~Full.Market.Value+Estimated.Expense, data = property)
summary(mymodel)

```
**Scatter Plot showing multivariate relationship between Estimated Gross Income,Full Market Value & Estimated Expense**

```{r}
ggplot(property)+geom_jitter(aes(x= log(Full.Market.Value+Estimated.Expense), y= log(Estimated.Gross.Income)))+geom_smooth(aes(x= log(Full.Market.Value+Estimated.Expense), y= log(Estimated.Gross.Income)), method ='lm', fill =NA)
```


**Liner corelation between Gross Square Feet & Full Market values**
**As the Gross Squre feet increases by log of 1 sqr.ft, the full market value also increases by log of 2.244e+02 dollar**
```{r}
ggplot(property)+geom_jitter(aes(x= log(Gross.SqFt), y= log(Full.Market.Value)))+geom_smooth(aes(x= log(Gross.SqFt), y= log(Full.Market.Value)), method ='lm', fill =NA)
```

**Liner corelation between Gross Square Feet & Full Market values**
** Equation: Full Market vaue = 2.244e+02 * Gross SquareFeet -2.400e+06 **

```{r}
mymodel = lm(Full.Market.Value~Gross.SqFt, data = property)
summary(mymodel)
```
**Replacing null values with mean values of the variable**
```{r}
property = mutate(property, Full.Market.Value = ifelse(is.na(Full.Market.Value), yes = mean(Full.Market.Value), no = Full.Market.Value))

property = mutate(property, Gross.SqFt = ifelse(is.na(Gross.SqFt), yes = mean(Gross.SqFt), no = Gross.SqFt))

```

**Leveraging the above equation for Knn**
**Step 1: Normalizing the values & defining input variables & label **
```{r}
input_variables = subset(property,select=c(Gross.SqFt,Full.Market.Value))

n_input_variables = sapply(input_variables, function(x){(x-min(x))/(max(x)-min(x))})

label = property$Building.Classification

input_n = data.frame(round(n_input_variables,2))
input_n


```

**knn**
**Model is abl to predict 85%(0.846) values correctly with the value of k = 5**
```{r}
set.seed(3635)
indices = sample(1:2, nrow(property), replace = T, prob = c(.8,.2))
training_input = input_n[indices==1,]
testing_input = input_n[indices == 2,]

training_label = label[indices==1]
testing_label = label[indices ==2]

#for(i in 1:80){

predictions = knn(train = training_input, test = testing_input, cl = training_label, k= 5)

p = sum(predictions == testing_label)/length(testing_label)
p
#print(str(i) + str(p))
#}
```

**Testing label had 1 R2-CONDOMINIUM value, model was not able to predict that correctly**
**Testing label had 33 R4-CONDOMINIUM values, model was able to predict all correctly**
**Testing label had 5 R9-CONDOMINIUM values, model was not able to predict none correctly**

```{r}
table(predictions, testing_label)
```
```{r}
table(testing_label)
```
```{r}
table(predictions)
```
```{r}
#library(caret)
confusionMatrix(table(predictions, testing_label))

```


**Adding a categorical variable to the model- Neigbouhood**
```{r}
class_dummies = model.matrix(~Neighborhood -1, data = property)
```
```{r}
input_n_with_class = data.frame(input_n,class_dummies)
input_n_with_class
```

**Knn with categorical variable **
**Model is abl to predict 76%(0.775) values correctly with the value of k = 5**
```{r}
set.seed(1234)
indices = sample(1:2,nrow(property), replace = T, prob=c(.8, .2) )

training_input = input_n_with_class[indices == 1,]
testing_input = input_n_with_class[indices == 2,]

training_label = label[indices==1]
testing_label = label[indices ==2]
```
```{r}
set.seed(12222)
predictions = knn(train = training_input, test = testing_input, cl = training_label, k= 5)
sum(predictions == testing_label)/length(testing_label)
table(predictions, testing_label)
```
```{r}

confusionMatrix(table(predictions, testing_label))
```

